---
title: "Causal Modelling Workshop - LAK23"
author: Ben Hicks and Joshua Weidlich
output:
  github_document:
    toc: true
    toc_depth: 3
---

More details to come, stay tuned! 

## Overview

This workshop will presented at the [Learning Analytics and Knowledge conference for 2023](https://www.solaresearch.org/events/lak/lak23/), in Arlington, Texas, USA.

We will explore how drawing diagrams such as the one below, called DAGs, can help understand causality and potential sources of bias (the DAG below is known as the 'butterfly bias').

``` {r echo = FALSE, fig.height = 3}
suppressWarnings(suppressPackageStartupMessages( library(dagitty)))
suppressWarnings(suppressPackageStartupMessages( library(ggdag)))

ggdag::butterfly_bias() %>% 
    ggdag() +
    theme_dag()
```

### About us

Ben Hicks : [twitter](https://twitter.com/benimbenix) 

Joshua Weidlich : [twitter](@hassenrueb)

## Preparation

The workshop is designed to allow for two streams: those interested in a general introduction into causal modelling and applications using pen and paper, and those also interested in the coding of the models, primarily using R. 

### Very very optional - R installation and packages

If you are interested in following some of the code examples we may cover, then make sure you have R (and preferably RStudio) installed prior to the workshop. The following code will install the required packages:

``` {r eval = FALSE}
install.packages("tidyverse")
install.packages("dagitty")
```

## Further reading

...to come.
